%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Kaidi Wang} % Your name
\address{Architecture Annex \\ 140 Otey St \\ Blacksburg, VA 24061 US} % Your address
% \address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(540)739-9577 \\ kaidi@vt.edu \\ kaidiw.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Ph.D. in Planning, Governance, and Globalization} \hfill {\em 2018-present} \\ 
Dissertation: The mutual effect between AV systems and cities: the role of urban forms, AV mode share and social interaction potential\\
Department of Urban Affairs and Planning\\
School of Public and International Affairs\\
Virginia Polytechnic Institute and State University\\
{\bf Computer and Information Sciences} \hfill {\em 2017-2018} \\ 
Department of Computer Science\\
College of Engineering\\
Virginia Polytechnic Institute and State University\\
{\bf M.S. in Information Security} \hfill {\em 2014-2017} \\ 
The Research Center of Information Security\\
School of Cyberspace Security\\
Beijing University of Posts and Telecommunications\\
{\bf B.S. in Information Security} \hfill {\em 2010-2014} \\ 
Department of Information Security\\
School of Telecommunications Engineering\\
Xidian University
\end{rSection}


\begin{rSection}{Research Interests}

Urban analytics; Emerging transportation technology; Big data and applied machine learning in urban studies; Geographic information systems.

% \begin{rSubsection}{ACME, Inc}{October 2010 - Present}{Web Developer}{Palo Alto, CA}
% \item Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec a diam lectus.
% \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Awards, Honors, and Fellowships}

First Grade Scholarship \hfill {\em 2014-2016} \\ 
Beijing University of Posts and Telecommunications

National Encouragement scholarship \textbf{Top 1\%} \hfill {\em 2013}\\
Xidian University

The postgraduate recommendation \textbf{Top 2\%} \hfill {\em 2013}\\
Xidian University

The Third Prize in the 24th Spark-Cup Undergraduate Academic and Technology Competition \hfill {\em 2013}\\
Xidian University

First Grade Scholarship \textbf{Top 8\%} \hfill {\em 2010-2012}



\end{rSection}


\begin{rSection}{Publications}


\begin{rSubSection}{Refereed Journal Articles}

{\bf Wang, K.}, \& Zhang, W. Parking Space Optimization in the Era of Private Automated Vehicles. Transportation Research Record. (Under Review)

{\bf Wang, K.}, W. Zhang, The Role of Urban Forms on the Performance of Shared Automated Vehicles (SAVs). Transportation Research Part D. (Accepted)

Zhang, W., {\bf Wang, K.}, Wang, S., Jiang, Z., Mondschein, A., \& Noland, R. B. (2020). Synthesizing neighborhood preferences for automated vehicles. Transportation Research Part C: Emerging Technologies, 120, 102774.

Zhang, W., \& {\bf Wang, K.} (2020). Parking futures: shared automated vehicles and parking demand reduction trajectories in Atlanta. Land Use Policy, 91, 103963.

\end{rSubSection}


\begin{rSubSection}{Peer-Reviewed Conference proceedings}

Jia, W., Chen T.D., W. Zhang, Lim, L., {\bf Wang, K.}, Mirla, A (2020). Willingness-toRelocate: Analyzing Travelers' Parking Preferences for Private Autonomous Vehicles. Transportation Research Board 100th Annual Meeting.

{\bf Wang, K.}, Zhang, W., Mortveit, H., \& Swarup, S. (2020). Improved Travel Demand Modeling with Synthetic Populations. The 21st International Workshop on Multi-Agent-Based Simulation (MABS2020).

{\bf Wang, K.}, Xie, W., \& Zhang, W. (2019). Parking Space Optimization in the Era of Private Automated Vehicles (No. 19-05868). Transportation Research Board 98th Annual Meeting.


\end{rSubSection}

\end{rSection}


\begin{rSection}{Teaching Experience}
{\bf Teaching Assistant} SPIA 3554 Transdisplinary Research Method\hfill {2021 Spring}\\
{\bf Teaching Assistant} SPIA 3554 Transdisplinary Research Method\hfill {2020 Spring}\\
{\bf Teaching Assistant} UAP3024 Urban and Regional Analysis \hfill {2019 Fall}\\
{\bf Teaching Assistant} SPIA3554 Transdisplinary Research Method \hfill {2019 Spring}\\
{\bf Teaching Assistant} Introduction to C++ programming \hfill {2017 Fall}\\

\end{rSection}

\begin{rSection}{Professional Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Urban Modeling & GIS, MATSim\\
Computer Languages & Python, R, CSS, HTML, Javascript \\
Tools & Git\\
\end{tabular}
\end{rSection}

\end{document}
